sensiAnPaper1All

### 2015-07-06 sensiAnPaper1All.Rmd
add to sensitivity analysis

```{r}
  library(resistance)

@@

  ## save results objects as rda for re-use
  save(listOutMix, file=paste(outFolder,'listOutMix.rda'))
  save(listOutI1, file=paste(outFolder,'listOutI1.rda'))
  save(listOutI2, file=paste(outFolder,'listOutI2.rda'))    
```

### now want to calculate the times to reach critical points and add them on to the input file 
### for different insecticide strategies, sequential, mix1 and mix2
```{r}
  #1) sequential : time to resistance for each insecticide in isolation
  #inputs : inAndOutI1, inAndOutI2
  #find time to criticalPoint for insecticide1
  #find time to criticalPoint for insecticide2
  #add together
  resistPoints1 <- findResistancePoints(listOutI1, locus=1)
  resistPoints2 <- findResistancePoints(listOutI2, locus=2)

  resistPointsSeq <- resistPoints1 + resistPoints2

@@

  #resistPointsMix2 <- findResistancePointsMixResponsive(listOutMix, listOutI1, listOutI2)
```

@@

  # easy to calc for which scenarios mixture1 is 'better' i.e. longer to resistance
  #boolean
  resistBetterMix1SeqBoolean <- resistPointsMix1 > resistPointsSeq
  #converted to 0/1
  resistBetterMix1Seq <- plyr::aaply(resistBetterMix1SeqBoolean,.margins=c(1,2),.fun=as.numeric)
  #rename rows ready for binding on to inputs
  rownames(resistBetterMix1Seq) <- gsub('gen','betterMix1Seq', rownames(resistBetterMix1Seq))

@@

>>>>

<!-- eval=FALSE to stop slow code being executed --> 
```{r, eval=FALSE}
  library(resistance)

@@

  ## save results objects as rda for re-use
  save(listOutMix, file=paste0(outFolder,'listOutMix.rda'))
  save(listOutI1, file=paste0(outFolder,'listOutI1.rda'))
  save(listOutI2, file=paste0(outFolder,'listOutI2.rda'))

  ## to load previously saved runs, e.g. these that I added 100 onto filename
  load(file=paste0(outFolder,'listOutMix_100.rda'))
  load(file=paste0(outFolder,'listOutI1_100.rda'))
  load(file=paste0(outFolder,'listOutI2_100.rda'))

### now want to calculate the times to reach critical points and add them on to the input file 
### for different insecticide strategies, sequential, mix1 and mix2
```{r}
  #1) sequential : time to resistance for each insecticide in isolation
  #inputs : inAndOutI1, inAndOutI2
  #find time to criticalPoint for insecticide1
  #find time to criticalPoint for insecticide2
  #add together
  resistPointsI1 <- findResistancePoints(listOutI1, locus=1)
  resistPointsI2 <- findResistancePoints(listOutI2, locus=2)

  resistPointsSeq <- resistPointsI1 + resistPointsI2

@@

  #resistPointsMix2 <- findResistancePointsMixResponsive(listOutMix, listOutI1, listOutI2)

  #4) mixture3 : time to resistance for both insecticides when used in a mixture
  #inputs : inAndOutMix
  #find time to criticalPoint for BOTH insecticide in mixture  
  resistPointsMix3 <- findResistancePoints(listOutMix, locus='both')

@@

  require('plyr')

  ## is mix1 better than sequential ?
  #T/F
  resistBetterMix1SeqBoolean <- resistPointsMix1 > resistPointsSeq
  #convert to 0/1
  resistBetterMix1Seq <- plyr::aaply(resistBetterMix1SeqBoolean,.margins=c(1,2),.fun=as.numeric)
  #rename rows ready for binding on to inputs
  rownames(resistBetterMix1Seq) <- gsub('gen','betterMix1Seq', rownames(resistBetterMix1Seq))

@@

  ## is mix3 better than sequential ?
  #T/F
  resistBetterMix3SeqBoolean <- resistPointsMix3 > resistPointsSeq
  #convert to 0/1
  resistBetterMix3Seq <- plyr::aaply(resistBetterMix3SeqBoolean,.margins=c(1,2),.fun=as.numeric)
  #rename rows ready for binding on to inputs
  rownames(resistBetterMix3Seq) <- gsub('gen','betterMix3Seq', rownames(resistBetterMix3Seq))

  #in 100 runs only one critical point run combination was mix3 better

  #check1
  #plot the 2 individual results & the mixture, just to check what is going on
  #the mixture one looks superficially similar to the individual ones superimposed
  x11()
  plotallele.freq.andy(listOutMix)
  x11()
  plotallele.freq.andy(listOutI1)
  x11()
  plotallele.freq.andy(listOutI2)

  #check2
  #what is the absolute difference between mix3 & sequential ?
  #looks plausible
  resistDifferenceMix3Seq <- resistPointsMix3 - resistPointsSeq

  #check3 is their a difference between the mix & the individual strategies
  #looks mostly plausible, occasionally there are 0s
  resistDifferenceMix1I1 <- resistPointsMix1 - resistPointsI1
  resistDifferenceMix1I2 <- resistPointsMix1 - resistPointsI2

  ## is mix2 better than sequential ?  
  # I might expect it to be similar to mix3
